Efficient Reversible Arithmetic Circuits using a Dirty Bit

### 2017-03-10 paper.tex
Half draft.

\documentclass[twocolumn]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\title{Efficient Reversible Arithmetic Circuits using a Dirty Bit}
\author{et al}

@@

\begin{abstract}
We describe classical and quantum circuits for performing reversible arithmetic using at most 1 ancilla in an unknown state.
Our constructions can perform incrementation, comparisons, addition, and modular addition with classical circuits of linear size and depth.
We also show how to perform modular offset, improving the best known space requirements for Shor's algorithm from $2n+2$ qubits to $2n+1$ qubits, in linear depth and $O(n \lg n)$ size.
\end{abstract}

@@

@@

As with addition and subtraction, you can turn an increment into a decrement either by reversing the gate order, by bordering the circuit with NOT gates, or by inverting all of the controls.
Also, increment gates can be controlled by using another invert-input-and-output trick (see figures \ref{} and \ref{}).

@@

\section{$O(N \lg N)$ Modular Addition and Offset}

@@

\begin{figure}
  \centering
  \includegraphics[totalheight=1.7cm]{modular-addition.png}
  \caption{\em Modular addition circuit.
  The $+r$ offset gates require $O(N \lg N)$ size.
  The pivot-flips require a dirty bit and that a constant.}
  \label{fig:modular-add}
\end{figure}

@@

@@

>>>>

\documentclass[twocolumn]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\title{Efficient Reversible Arithmetic Circuits using a Dirty Bit}
\author{Craig Gidney}

@@

\begin{abstract}
\em
We present efficient quantum and reversible classical circuits for performing incrementation, addition, comparisons, modular addition, and modular offset using no ancilla or 1 ancilla in an unknown state.
We use these circuits to improve the best known space requirements for Shor's algorithm from $2n+2$ qubits to $2n+1$ qubits, without increasing the depth or size complexity.
[[[FIND OTHER APPLICATIONS]]]
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics[totalheight=4cm]{fourier-addition.png}
  \caption{\em Controlled-increment from fourier addition. [[[NOT MENTIONED]]] [[[CITE THE PAPER THAT INTRODUCED THE IDEA]]]}
  \label{fig:fourier-addition}
\end{figure}

@@

As with addition and subtraction, you can turn an increment into a decrement either by reversing the gate order, by bordering the circuit with NOT gates, or by inverting all of the controls.
Also, increment gates can be controlled by using another invert-input-and-output trick (see figures \ref{fig:controlled-increment-odd} and \ref{fig:controlled-increment-even}).

\begin{figure}
  \centering
  \includegraphics[totalheight=2cm]{controlled-increment-odd.png}
  \caption{\em Odd-sized $O(N)$ controlled increment with 1 dirty ancilla.}
  \label{fig:controlled-increment-odd}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[totalheight=2.5cm]{controlled-increment-even.png}
  \caption{\em Even-sized $O(N)$ controlled increment with 1 dirty ancilla.}
  \label{fig:controlled-increment-even}
\end{figure}

@@

\section{$O(N \lg N)$ Modular Addition and Modular Offset}

@@

\begin{figure}
  \centering
  \includegraphics[totalheight=1.7cm]{modular-addition.png}
  \caption{\em Modular addition circuit.
  The $+r$ offset gates require $O(N \lg N)$ size.
  The pivot-flips require a dirty bit.}
  \label{fig:modular-add}
\end{figure}

@@

[[[Surely there are more? Need to look around.]]]

\section{Conclusion}

[[[TODO]]]

@@

[[[Surely there are more?]]]

[[[Previous paper constructing each type of circuit shown here, and how they compare.]]]
